pirouette: Quantifying the importance of a tree prior in Bayesian phylogenetics

### 2019-03-13 article.tex
Doing nicely reviewing ERQ 2

Due to sensible defaults, specifying this
results in:

@@

@@

"What is the error made by BEAST2 from a phylogeny when
picking the best inference model?"

@@

In the second step we state our experiments. 
Within this example, all our experiments are candidates,
run only if it is the best candidate, the evidence is measured (ignoring
this will give a helpful error) and we use the full set of 
40 inference models, which are all combinations of 4 site 
models, 2 clock models and 5 tree priors.

@@

Also here, the third (the BEAST2 inference) and fourth (measuring the error)
steps have sensible defaults, and we are not
interested in using a twin tree. We can create the complete
\verb;pirouette; parameter set (again) like this:

>>>>

Listing~\ref{lst:create_generative_experiment_explicit} shows how to
set up this experiment:

@@

There are more ways to pick a standard inference model. In the
previous example, we picked the known generative inference model.
A novel tree prior, by definition, is non-standard, thus cannot be
part of a standard inference model. 
One option is to choose to hand-pick a related 
standard tree prior, as done in ERCs 3 and 5, and combine it with 
a known generative alignment model.
An alternative is to let multiple candidate inference models compete 
and pick the best one, based on the highest evidence (aka marginal likelihood):
when an alignment is simulated from the given tree, one can estimate the
evidence for each inference model given that 
alignment \richel{or the other way around?}.
The benefit of this approach is that this is a commonly used procedure,
which picks an inference model that is
best at explaining the alignment, where more complex inference models are
penalized for having more parameters.

@@

"What is the inference error made on a novel phylogeny when
picking the best inference model?"

@@

In the second step we set up our experiments. 
Within this ERQ, each of our experiments contain a different
inference model $I$, but has condition $C$ that will only let $I$
be run in inference if that inference model $I$ is the 
best candidate inference model, that is, 
it is the inference model with the highest evidence.
Setting up experiments like this is thought to be so common,
that \verb;pirouette; has a simple function to do:
\verb;create_all_experiments; will create 40 experiments,
containing inference models of all combinations of 4 site 
models, 2 clock models and 5 tree priors.

@@

For all other steps we use the default setups. 
We can create the complete
\verb;pirouette; parameter set like this:
